Current and future constraints on primordial magnetic fields

### 2017-07-24 pmf.tex
beta scalin response

\changed{The power in the tensor modes also depends on the timing of PMF generation relative to neutrino decoupling. 
We evaluate the tensor power predicted by the \citet{zucca16} code while stepping $\beta$ by two from 2 to 20, and find it scales as $\beta^{1.9}$ to an excellent approximation. 
We use this $\beta$ power law form to handle the PMF timing dependence. 
Thus the tensor PMF power will scale as:
\be \label{eqn:betascaling}
\apmf^{tens} \propto  \bpmf^4 \beta^{1.9},
\ee
}

>>>>

\changed{The power in the tensor modes also depends on the timing of PMF generation relative to neutrino decoupling, and is expected to scale approximately as $\beta^2$ \citep{lewis04,shaw10b}.   
We double-check this expectation for $\beta$ in the range 2 to 20 using the  \citet{zucca16} code, and find the computed tensor power scales as $\beta^{1.9}$
We use this $\beta$ power law form to handle the PMF timing dependence. 
Thus the tensor PMF power will scale as:
\be \label{eqn:betascaling}
\apmf^{tens} \propto  \bpmf^4 \beta^{1.9},
\ee
}
